### 2023-06-20 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass should be restricted
  to the DIS region, $Q^2 \ge 2$ GeV$^2$ and $W^2 \ge 12.5$ GeV$^2$.
  %
  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
  be that of Run III while for the FPF experiments we assume the full HL-LHC
  luminosity (3 ab$^{-1}$).
  %
   The numbers in parenthesis indicate the event rates corresponding to charm
  production for those experiments with heavy flavour tagging capabilities.

@@

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=1\textwidth]{plots/Nevent_FASERv2_14.pdf}
    \caption{Event rate per bin for muon neutrinos at FASER$\nu$2. Bins are denoted by dashed grid, and the red dot indicates the weighted average of $x,Q^2$ points in each bin. The total number of muon neutrino events calculated is $\approx2.6\times 10^5$. Note that bins were chosen somewhat arbitrarily, and can be iterated to improve PDF fits }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

where $f(x_i,Q^2_i,E_{\nu ,i}) = \frac{dN_{\nu}}{dE_{\nu,i}}\left(\frac{d^2\sigma(x_i,Q^2_i,E_{\nu,i})}{dxdQ^2}\right)$.

The statistical uncertainty for each bin is then defined by a Gaussian distribution with fractional uncertainty $1/\sqrt{N{\rm ev}/{\rm bin}}$, i.e. $\delta N_{\rm ev}/{\rm bin} = \sqrt{N_{\rm ev}} /{\rm bin}$

  Following this prescription, we can produce plots which characterize the event rate for a particular neutrino species at a particular experiment.

Results for FASER$\nu$2 can be found \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results}{here}. The .txt files will display which neutrino species was considered, and also compile experimental geometries and target details in the header. In the sub-folder \href{https://github.com/juanrojochacon/FPF-WG1/tree/main/results/Summaries}{summaries}, plots can be found which show the event rate in $x,Q^2$ space, integrating over the entire neutrino spectrum. The event rate for muon neutrinos at FASER$\nu$2 is shown in Fig~\ref{fig:fasernu2_muon}.

charm production

\subsection{Estimating systematic uncertainties}

We now wish to understand the impact of systematic uncertainties on the event rate in $(x,Q^2,E_{\nu})$ space. For each experiment, the observables $E_{l},E_{h},\theta$ are related to $(x,Q^2,E_{\nu})$ by

\begin{align}
E_{\nu} = E_l + E_h \nonumber \\
Q^2 = 4E_lE_{\nu}\sin^2{\theta/2} \nonumber \\
x = \frac{Q^2}{2m_N(E_{\nu} - E_l)}.
\end{align}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width = 1\textwidth]{plots/error_plot_FASERv2_14.pdf}
    \caption{Event rates with error bars at FASER$\nu$2 for $\nu_{\mu} N \rightarrow \mu^- X$} summed over $Q^2$. The error bars along the x-axis showing the width of the $x$-bins, and are not showing any type of error.
    \label{fig:my_label}
\end{figure}

>>>>

Table~\ref{tab:integrated_rates} summarises the predicted integrated event yields for the five detectors considered
  in the present analysis, separated into electron neutrinos and antineutrinos
  and muon neutrinos and antineutrinos.
  %
  These event yields are computed from Eq.~(\ref{eq:event_yields}) with the only
  restriction that the momentum transfer and the final-state invariant mass should be restricted
  to the DIS region,
  \be
  \label{eq:DISconditions}
Q^2 \ge 2~{\rm GeV}^2\quad{\rm and} W^2 \ge 12.5~{\rm GeV}^2 \, .
\ee
  %
  As discussed above, for FASER$\nu$ and SND@LHC we assume the integrated luminosity to
  be that of Run III while for the FPF experiments we assume the full HL-LHC
  luminosity (3 ab$^{-1}$).
  %
   The numbers in parenthesis indicate the event rates corresponding to charm
  production for those experiments with heavy flavour tagging capabilities.

@@

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos detected at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrated over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos as indicated in Table~\ref{tab:integrated_rates}.
  %
  Kinematic cuts are such that the DIS conditions Eq.~(\ref{eq:DISconditions}) are satisfied.
  %
  Only bins with at least 30 events are retained.
  %
  One can observe the large event rates for most of the region in $\lp x,Q^2\rp$ covered,
  which result into very competitive statistical uncertainties.
  %
  From Fig.~\ref{fig:fasernu2_muon} we see that the kinematic coverage of FASER$\nu$2 is
  $x_{\rm min}\sim 10^{-3}$ at small-$x$ and $Q^2_{\rm max}\sim 10^4$ at large-$Q^2$, which represent an extension
  of around one order of magnitude in both directions as compared to available
  DIS neutrino data.

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
\includegraphics[width=0.9\textwidth]{plots/Nevent_FASERv2_14.pdf}
\caption{The event yields per bin $ N_{\rm ev}^{(i)}$,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos at FASER$\nu$2.
  %
  We present results binned in $x$ and $Q^2$ and integrating over the neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into $N_{\rm ev}(\nu_\mu)\sim 3\times 10^5 $ reconstructed muon
  neutrinos. }
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated
statistical uncertainty in each bin
\be
\label{eq:statistical_uncertainties}
\delta_{\rm stat}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since here we discard bins with less than 30 events, this statistical uncertainty
ranges between $\sim 1\%$ and $\sim 18\%$ for muon neutrinos in FASER$\nu$2 depending on the values of
$x$ and $Q^2$ associated to this bin.
%
These statistical uncertainties are displayed in the left panel
of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
to the same event yields as in
Fig.~\ref{fig:fasernu2_muon}
now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
%
The error bar in the $y$-direction indicates the statistical uncertainties, while
that in the $x$ direction corresponds to the width of the $x$-bins.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = 0.95\textwidth]{plots/error_plot_FASERv2_14.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon}
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$.
      %
      In addition to the event yields we show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The error bars in the $x$ direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Systematic uncertainties}

In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
one needs to estimate the systematic uncertainties associated to the reconstruction
of the final state leptonic and hadronic variables as listed in Table~\ref{tab:FPF_experiments}.
%
For instance, an event which would be classified in a given bin in the case
of a perfect detector may end up in a different bin in the presence of systematic
shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
hadronic energy $E_h$.
%
Hence, for each source of experimental systematic uncertainty we would like to estimate
its impact at the level of event yields and eventually stablish also the associated
correlation matrix.

By means of tree-level DIS kinematics one can relate the variables describing the neutrino-nucleon
hard-scattering, $(x,Q^2,E_{\nu})$,
with those describing the leptonic and hadronic final state, namely $\lp E_{\ell},\theta_\ell, E_{h} \rp$,
and that correspond to experimentally measured quantities.
%
The mapping between the two sets of variables is 
\bea
E_{\nu} &=& E_\ell + E_h \, ,\nonumber \\
Q^2 &=& 4E_\ell E_{\nu}\sin^2\lp {\theta_\ell/2}\rp  =  4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp \, , \\
x &=& \frac{Q^2}{2m_N(E_{\nu} - E_\ell)} = \frac{4E_\ell \lp E_\ell + E_h  \rp\sin^2\lp {\theta_\ell/2}\rp}{2m_NE_{h}} \, , \nonumber
\eea
highlighting how the measurement of $E_{\ell}$, $\theta_\ell$, and $E_{h}$ uniquely specify the hard-scattering
kinematics $(x,Q^2,E_{\nu})$ of the event.
%
Therefore, systematic uncertainties in the measurement of these final-state variables will modify
the assignbment of each event to a given bin of $x$, $Q^$, and $E_\mu$ introducing a systematic
error in the event yields and hence in the measurement of the double-differemtial
neutrino scattering cross-section.

@@

\subsection{Pseudo-data generation}
